Cognate Priming: Report

### 2021-10-07 Rmd/report_03_data-analysis.Rmd
Update README.md with new instructions, add new analyses to Rmd , remove redundant files, and update targets
Render report

## Data analysis

@@

contrasts(gaze$trial_type) %>% 
	as.data.frame() %>% 
	set_names(paste0("trial_type", 1:2)) %>% 
	rownames_to_column("level") %>% 
	gt(rowname_col = "level")

>>>>

@@

contrasts(gaze$trial_type) %>% 
	as.data.frame() %>% 
	set_names(paste0("trial_type", 1:2)) %>% 
	rownames_to_column("level") %>% 
	gt(rowname_col = "level") %>%
	as_raw_html()

### 2021-10-07 Rmd/report_04_gca_relaxed.Rmd
Render report

$$
\log(\frac{p}{n - q}) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
$$

@@

draws %>% 
	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95, 1))))) +
	geom_vline(xintercept = 0) +
	stat_halfeye() +
	labs(x = "Value", y = "Variable", fill = "CrI") +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	theme(
		axis.title = element_blank(),
		legend.position = "top"
	)

@@

vcov(fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Mean post. correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text = element_text(hjust = 1, size = 8),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
	)

@@

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_hline(yintercept = 0.5) +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.75) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
							   colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 1, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 9)
	)
```

>>>>

$$

\color{white}{
\log \Bigg( \frac{p}{n - q} \Bigg) = (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
(\beta_{1} + \beta_{1p} + \beta_{1i}) \times Age_{pi} + ... \\
(\beta_{2} + \beta_{2p} + \beta_{2i}) \times Vocabulary_{pi} + ... \\
(\beta_{3} + \beta_{3p} + \beta_{3i})\times Condition_{pi} + ... \\
(\beta_{4} + \beta_{4i}) \times Group_{pi} + ... \\
(\beta_{5} + \beta_{5i}) \times (Vocabulary_{pi} \times Group_{pi}) + ... \\
(\beta_{6} + \beta_{6i}) \times (Vocabulary_{pi} \times Condition_{pi}) + ... \\
(\beta_{7} + \beta_{7i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
(\beta_{8} + \beta_{8i}) \times (Vocabulary_{pi} \times Group_{pi} \times Condition_{pi}) + \varepsilon_{pi}
}
$$

@@

draws %>% 
	filter(!str_detect(.variable, "time_bin|sigma")) %>% 
	mutate(.value = ifelse(.variable=="b_Intercept", inv_logit_scaled(.value), .value/4)) %>% 
	ggplot(aes(.value, .variable, fill = stat(cut_cdf_qi(cdf, labels = percent, .width = c(0.50, 0.80, 0.95))))) +
	geom_vline(xintercept = 0, colour = "white") +
	stat_halfeye(point_color = "white", interval_color = "white") +
	labs(x = "Value", y = "Variable", fill = "CrI") +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	theme(
		axis.title = element_blank(),
		legend.position = "top"
	)

@@

vcov(fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

@@

ggplot(m, aes(time_bin_center, .value)) +
	facet_wrap(~fct_rev(lp)) +
	geom_hline(yintercept = 0.5, colour = "white") +
	geom_line(aes(group = interaction(age_group, trial_type, lp, .draw),
				  colour = trial_type),
			  alpha = 0.15, size = 0.65) +
	stat_summary(aes(group = trial_type, colour = trial_type),
				 fun = mean, geom = "line", size = 1.25) +
	stat_summary(data = gaze_relaxed, aes(y = logit_to_prob(logit_adjusted), group = trial_type,
										  colour = trial_type),
				 fun.data = mean_se, geom = "errorbar", size = 0.5, na.rm = TRUE,
				 position = position_dodge(width = 0.3)) +
	geom_text(data = sample_size, aes(x = min(gaze_relaxed$time_bin_center), y = 0.95, label = paste0("N = ", n)),
			  colour = "white", hjust = 0, size = 5) +
	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_x_continuous(breaks = min(gaze_relaxed$time_bin_center):max(gaze_relaxed$time_bin_center), labels = unique(gaze_relaxed$time_bin)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 9),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank()
	)
```
